### 2015-12-14 conclusions.tex
Mention Pistol and fixes

We have investigated scale-free algorithms for online linear optimization and
we have shown that scale-free property leads to algorithms which have optimal
regret and do not need to know or assume \textbf{anything} about the sequence
of loss vectors, i.e. without any assumption on the norms of the loss vectors
and the number of rounds. We have designed two scale-free algorithms for online
linear optimization with regret bound $O \left(\sqrt{\sup_{v \in K} f(v)
\sum_{t=1}^T \|\ell\|_*^2} \right)$ where $f$ is any non-negative $1$-strongly
convex function with respect to a norm $\|\cdot\|$ defined on the decision set
and where $\|\cdot\|_*$ is the dual norm to $\|\cdot\|$.  These algorithms are
based on \textsc{Follow The Regularizer Leader}.  We have shown that one of the
algorithms has regret $O \left(f(u) \sqrt{\sum_{t=1}^T \|\ell_t\|_*^2} +
\max_{t=1,2,\dots,T} \|\ell_t\|_* \sqrt{T} \right)$ with respect to any
competitor $u \in K$, where $f$ is any non-negative $1$-strongly convex
function defined on the decision set.  The latter result makes sense even when
the decision set $K$ is unbounded.

@@

>>>>

We have investigated scale-free algorithms for online linear optimization and
we have shown that scale-free property leads to algorithms which have optimal
regret and do not need to know or assume \textbf{anything} about the sequence
of loss vectors. In particular, the algorithms do not assume any upper or lower
bounds on the norms of the loss vectors or the number of rounds.

We have designed two scale-free algorithms based on \textsc{Follow The
Regularizer Leader}.  Their regret is $O \left(\sqrt{\sup_{v \in K} f(v)
\sum_{t=1}^T \|\ell\|_*^2} \right)$ where $f$ is any non-negative $1$-strongly
convex function with respect to a norm $\|\cdot\|$ defined on the decision set
and where $\|\cdot\|_*$ is the dual norm to $\|\cdot\|$.

@@

We have shown that one of the scale-free \textsc{FTRL}-based the algorithms has
regret $O \left(f(u) \sqrt{\sum_{t=1}^T \|\ell_t\|_*^2} + \max_{t=1,2,\dots,T}
\|\ell_t\|_* \sqrt{T} \right)$ with respect to any competitor $u \in K$, where
$f$ is any non-negative $1$-strongly convex function defined on the decision
set.  The latter result makes sense even when the decision set $K$ is
unbounded. Notice that with regularizer $f(w) = \frac{1}{2}\|w\|_2^2$ the
regret depends on norm of the competitor $\|u\|_2$ is quadratically. There
exist non-scale-free algorithms \cite{ McMahan-Streeter-2012,
McMahan-Abernethy-2013, Orabona-2013, McMahan-Orabona-2014, Orabona-2014} that
have only $O(\|u\|_2 \sqrt{\log \|u_2\|_2})$ or $O(\|u\|_2 \log \|u\|_2)$
dependency.  These algorithms, however, assume an a priori bound on the norm of
the loss vectors.  This leads to another open problem:
%
\begin{quotation}
\noindent
\emph{Design a scale-free algorithm that has $O(\|u\|_2 \sqrt{\log \|u\|_2})$
dependency on the norm $\|u\|_2$ of the competitor.}
\end{quotation}

### 2015-12-14 introduction.tex
Mention Pistol and fixes

Majority of existing algorithms for OLO are based on two generic algorithms:
\textsc{Follow The Regularizer Leader} (\textsc{FTRL}) and \textsc{Mirror
Descent} (\textsc{MD}). \textsc{FTRL} dates back to the potential-based
forecaster in \cite[Chapters~11]{Cesa-Bianchi-Lugosi-2006} and its theory was
developed in \cite{Shalev-Shwartz-2007}.  The name \textsc{Follow The
Regularized Leader} comes from~\cite{Abernethy-Hazan-Rakhlin-2008}.
Independently, the same algorithm was proposed in~\cite{Nestorov-2009} for
convex optimization under the name \textsc{Dual Averaging} and later
rediscovered in~\cite{Xiao-2010} for online convex optimization. The general
version with time-varying regularizers was analyzed in
\cite{Orabona-Crammer-Cesa-Bianchi-2014}. \textsc{MD} was originally proposed
in \cite{Nemirovski-Yudin-1983} and later analyzed in~\cite{Beck-Teboulle-2003}
for convex optimization. In the online learning literature it makes the first
appearance, under a different name, in \cite{Kivinen-Warmuth-1997}. Good
description of \textsc{MD} is given in~\cite{Rakhlin-Sridharan-2009}.

@@

For unbounded decision sets no scale-free algorithm with a non-trivial regret
bound was known. Unbounded decision sets are practically important, since
learning large-scale linear models (e.g. logistic regression) is done by
reducing it to OLO with decision set $\R^d$.

@@

Our proof technique are also new because they rely on new homogeneous
inequalities (Lemmas~\ref{lemma:recurrence-solution}, \ref{lemma:useful}).

Finally, in Section~\ref{subsection:mirror-descent-lower-bound}, we show
negative results for existing popular variants of \textsc{MD}. We show that
variants of \textsc{MD} have $\Omega(T)$ regret if the Bregman divergence
associated with the regularizer is unbounded.  The setting includes the
standard gradient descent with step size $1/\sqrt{t}$, \textsc{AdaGrad MD} and
\textsc{Scale-Free MD} on a unbounded decision set. This result suggests that
\textsc{FTRL} is superior to \textsc{MD}.

>>>>

Majority of existing algorithms for OLO are based on two generic algorithms:
\textsc{Follow The Regularizer Leader} (\textsc{FTRL}) and \textsc{Mirror
Descent} (\textsc{MD}). \textsc{FTRL} dates back to the potential-based
forecaster in \cite[Chapter~11]{Cesa-Bianchi-Lugosi-2006} and its theory was
developed in \cite{Shalev-Shwartz-2007}.  The name \textsc{Follow The
Regularized Leader} comes from~\cite{Abernethy-Hazan-Rakhlin-2008}.
Independently, the same algorithm was proposed in~\cite{Nestorov-2009} for
convex optimization under the name \textsc{Dual Averaging} and later
rediscovered in~\cite{Xiao-2010} for online convex optimization. The general
version with time-varying regularizers was analyzed in
\cite{Orabona-Crammer-Cesa-Bianchi-2014}. \textsc{MD} was originally proposed
in \cite{Nemirovski-Yudin-1983} and later analyzed in~\cite{Beck-Teboulle-2003}
for convex optimization. In the online learning literature it makes the first
appearance, under a different name, in \cite{Kivinen-Warmuth-1997}. Good
description of \textsc{MD} is given in~\cite{Rakhlin-Sridharan-2009}.

@@

For unbounded decision sets no scale-free algorithm with a non-trivial regret
bound was known. Unbounded decision sets are practically important, since
learning of large-scale linear models (e.g. logistic regression) is done by
gradient methods that can be reduced to OLO with decision set $\R^d$.

@@

Our proof techniques rely on new homogeneous
inequalities (Lemmas~\ref{lemma:recurrence-solution}, \ref{lemma:useful})
which might be of independent interest.

Finally, in Section~\ref{subsection:mirror-descent-lower-bound}, we show
negative results for existing popular variants of \textsc{MD}. We show two
examples that demonstrate variants of \textsc{MD} can have $\Omega(T)$ regret
(on sequences of loss vector of unit norm) if the Bregman divergence associated
with the regularizer is unbounded.  First example demonstrates
$\Omega(T^{3/2})$ regret of the standard gradient descent with step size
$1/\sqrt{t}$, \textsc{AdaGrad MD} and \textsc{Scale-Free MD} on a unbounded
decision set.  Second example demonstrates $\Omega(T)$ regret for
\textsc{Scale-Free MD} for learning with expert advice with negative entropy
regularizer.  Both results indicate that \textsc{FTRL} is superior to
\textsc{MD}.
